\vspace*{-40pt}
%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Phitchawat Lukkanathiti}}\\
	\faMapMarker \vspace{0.4mm} Bangkok, Thailand $\cdot$ \faEnvelope \vspace{0.4mm} me@phitchaw.at $\cdot$ \faPhone \vspace{0.4mm} +66 (0) 89 413 4748 \\
  \faGlobe \vspace{0.4mm} https://phitchaw.at $\cdot$ \faLinkedinSquare \vspace{0.4mm} linkedin.com/in/phitchawat $\cdot$ \faGithub \vspace{0.4mm} Shayennn\\
\vspace{-2mm}
{\tiny{RESUMEVERSION compiled on \today. See the latest version at \href{https://github.com/Shayennn/resume/releases/latest/download/Phitchawat_Lukkanathiti_Resume_with_transcript.pdf}{phitchaw.at/resume}}}\\
\vspace{2mm}
        I am a highly skilled IT Generalist who believes in automation and is interested in software engineering, computer architecture, cloud computing, and aviation.
\end{center}
\vspace{2mm}

%==== Education ====%
\header{Education}
\textbf{Kasetsart University}\hfill Bangkok, Thailand\\
B.Eng. (Computer Engineering) (Second Class Honors) \textit{GPA: 3.42} \hfill Aug 2018 - Apr 2022\\
Senior Project: \textit{Optimizing and Deploy WebODM on Kubernetes Cluster on Bare-metal server}\\
\vspace{2mm}

%==== Experience ====%
\header{Work Experience}
\vspace{1mm}

\textbf{LINE Pay (Thailand) / LINE MAN Wongnai Co., Ltd.} \hfill Bangkok, Thailand\\
\textit{Site Reliability Engineer} \hfill Jan 2024 - Present\\
\vspace{-1mm}
\begin{outline}
	\1 Focus on Site Reliability Engineering (SRE), DevOps, Infrastructure as Code (IaC), System Administration, etc.
\end{outline}
\vspace{-1mm}
\textbf{Merkle Capital Co., Ltd. \textit{\tiny{(The Cryptomind Group Holding subsidiary company.)}}} \hfill Bangkok, Thailand\\
\textit{Senior Full-Stack Software Engineer / Developer} \hfill Oct 2023 - Jan 2024 (4M)\\
\vspace{-1mm}
\begin{outline}
	\1 Hiring Manager (de facto, on behalf of CTO), manages software engineer interview process, interviews candidates, and onboards new hires.
	\1 Rapidly Responded to and Mitigated a Critical DDoS Attack (Duration: 1 hour)
	\1 Recovered from an Accidental Virtual Machines Deletion (Duration: 2 hours)
	\1 Optimized CI/CD Pipeline, Reduced Running Time from 30 minutes to 12 minutes (Reduced 18 minutes)
	\1 Enforced Security Policies, Fully SSL PostgreSQL Connection, etc.
	\1 Setup Background Task System with Bull and Redis
\end{outline}
\vspace{-1mm}
\textit{Full-Stack Software Engineer / Developer} \hfill Oct 2022 - Sep 2023 (12M)\\
\vspace{-1mm}
\begin{outline}
	\1 Develop and Maintain the Company's Main Product (Digital Asset Management Platforms)
		\2 Improved KYC Liveness Detection with 3rd Party Integration (Verifio)
		\2 Developed Fund Switching Feature
		\2 Optimized CI/CD Pipeline, Cypress Test, etc.
	\1 Develop and Maintain internal systems
		\2 Maintain WiFi Hotspot and Logging system at both two offices (Dragon Town and MitrTown)
		\2 Setting up Mock Phishing for Crypromind Group
		\2 Setting Up Outgoing Proxy Server for Merkle and Elkrem
\end{outline}
\vspace{-1mm}
\textit{Project Manager} \textit{\tiny (Project-based Outsourcing under D.E. Wellington Technologies Co., Ltd.)} \hfill June 2022 - Sep 2022 (4M)\\
\vspace{-1mm}
\begin{itemize}
	\item Develop Trading Terminal Platform for Merkle Capital Co., Ltd.
	\item My team has 1 Project Manager, 4 Developers, 2 QAs, and 1 UX/UI Designer.
	\item Also doing a part of other roles which are Technical leader, DevOps, System Architect, Product Owner, and Scrum Master.
\end{itemize}
\vspace{-1mm}
\textbf{LINE MAN Wongnai Co., Ltd.} \hfill Bangkok, Thailand\\
\textit{Site Reliability Engineer (Part-time)} \hfill Apr 2022 - Sep 2022 (6M)\\
\vspace{-1mm}
\begin{itemize}
	\item Migrate a part from Huawei Cloud to AWS
	\item Working on Gitlab CI to support single-branch workflow
	\item Log collector and summarize script for tech-infra auditing
\end{itemize}
\vspace{-1mm}
\textbf{ExxonMobil Corporation} \hfill Bangkok, Thailand\\
\textit{Platform Engineering Intern} \hfill May 2021 - Nov 2021 (7M)\\
\vspace{-1mm}
\begin{itemize}
	\item QA (Quality Assurance) on POS (Point of Sale) System
	\item PoC (Proof of Concept) of Automation Testing for POS System
	\item Retail batch close validation error investigation
	\item Make a script to investigate batch close errors which can reduce the time from 20 days to 2 hours
\end{itemize}
\vspace{-1mm}
\textbf{Freelancer / Outsourcing} \hfill 2014 - Present\\
\textit{Developer, Project Manager, Software Engineer}\\
\vspace{-1mm}
\begin{outline}
	    \1 Alternetive Line Official Accounts Management Panel - Cheaper broadcasting system, Admin Panel, etc.
	    \1 KOBBank - Bank transactions crawler software as a service.
		\1 Drone Images Processing 
			\2 Live Video Processing on Drone Embedded System
			\2 Crop Health Analysis
			\2 Orthophoto
			\2 3D Pointcloud
\end{outline}
\vspace{2mm}

%==== Skills ====%
\header{Skills}
\begin{tabular}{ l l }
	Programming Languages: & Python, Golang, JavaScript, TypeScript, C, HTML, CSS, JSONNet                         \\
	Frameworks:            & FastAPI, Flask, React.js, Express, Django, Firebase, Laravel, CodeIgniter,  \\ & Celery        \\
	Libraries:             & Tailwind CSS, jQuery, Bootstrap                                                          \\
	Databases:             & MySQL, MariaDB, PostgreSQL, MongoDB, Firebase Firestore, \\ & Firebase Realtime Database      \\
	Dev Tools:             & VSCode, GoLand, PyCharm, Git, GitHub, GitLab                                                    \\
	System\&Infra:         & Linux, Docker, Kubernetes, Terraform, Google Cloud Platform (GCP), \\ & Amazon Web Services (AWS), Redis, Bash \\
\end{tabular}
\vspace{2mm}

%==== Projects ====%
\header{Projects}
{\textbf{2024 - CloudPBX / Telephone System}} {\sl FreePBX, SIP} \\
PBX system for Merkle Capital Co., Ltd. and Cryptomind Group \\
\vspace*{2mm}
{\textbf{2022 - Trading Terminal for Merkle Capital Co., Ltd.}} {\sl Python, Django, Celery, JavaScript, React.js, Redis, Docker, Google Cloud Platform (GCP), Terraform, Git, Github} \\
A system to manage Merkle Capital assets, cryptocurrencies, and digital tokens.\\
Project Value: 1,300,000 THB\\
\vspace*{2mm}
{\textbf{2021 - WiFi Hotspot and Logging system}} {\sl Mikrotik, Synology NAS} \\
WiFi Hotspot system for Merkle Capital Co., Ltd. which collect traffic log and is all done with Mikrotik and NAS\\
Cost reduction: ~30,000 THB from Market Price\\
\vspace*{2mm}
{\textbf{2020 - KUFillingGood}} {\sl Firebase, JavaScript, Google Cloud Storage} \hfill https://kufg.phitchaw.at\\
3rd party Kasetsart University class registration advisory system\\
Man-hour reduction: 30,000 MH to less than 10,000 MH (approximate calculation, 3h x 10k Bangkhen students)\\
\vspace*{2mm}
{\textbf{2014 - KOBBank}} {\sl PHP, CodeIgniter, JavaScript, Socket.io} \hfill https://phitchaw.at/bank\\
Bank transactions crawler software solution. Serve as software as a service (SaaS)\\
Project Value: > 2,400,000 THB\\
License Count: > 400 licenses (Active 89 License)\\
\vspace*{2mm}
{\textbf{2014 - KOBBank Admin Panel}} {\sl PHP, Google Cloud Platform (GCP), Memcached, Python, Flask, PyTorch, MariaDB} \\
Licensing, Management, and Billing System for KOBBank\\
\vspace{2mm}

%==== Awards ====%
\header{Awards}
\textbf{1st place in KPMG Cyber Security Challenge 2021} \hfill KPMG (Thailand)\\
Recognized as team leader of Kaidonjai \hfill Oct 2021\\
\vspace*{2mm}
\textbf{1st place in ASEAN group of ASCIS2021} \hfill ASEAN Student Contest on Information Security\\
Recognized as team leader of IDK IDK IDK \hfill Nov 2021\\
\vspace*{2mm}
\textbf{1st place in Thailand Cyber Top Student 2021} \hfill National Cyber Security Agency\\
Recognized as team leader of IDK IDK IDK \hfill Aug 2021\\
\vspace*{2mm}
\textbf{First Prize in ASC 20-21} \hfill Asia Supercomputer Community\\
ASC Student Supercomputer Challenge\\
Recognized for optimizing QuEST (Quantum Exact Simulation Toolkit) and Infrastructure preparation. \hfill May 2021\\
\vspace*{2mm}
\textbf{2nd place in Financial Cybersecurity Bootcamp 2020} \hfill The Thai Bankers\textquotesingle{} Association\\
The CTF and vision of cybersecurity competition by Bank of Thailand, Securities and Exchange Commission, Office of Insurance Commission, Electronic Transactions Development Agency, and The Thai Bankers\textquotesingle{} Association \hfill Nov 2020\\
\vspace*{2mm}
\textbf{2nd place of Thailand Cyber Top Talent 2022 (Senior Level)} \hfill National Cyber Security Agency\\
Recognized as a member of Blueberry \hfill Nov 2022\\
\vspace{2mm}

%==== Languages ====%
\header{Languages}
\begin{tabular}{ l l }
	Thai: & Native Speaker\\
	English:            & 820 of 990 of TOEIC on June 2024\\
\end{tabular}
\vspace{2mm}
